---
title: "Segundo examen, Brayan Reyes 1950182"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Planta de oxidacion

en este informe del segundo examen de diseño experimental procesaremos la informacion de la base de datos stackloss y daremos el respectivo analisis a dichos datos.
```{r}
data(stackloss)
```


## Including Code

You can include R code in the document as follows:

```{r}
library(dplyr)
data(stackloss)
stackloss<- mutate(stackloss, concentracion= (Acid.Conc./10)+50)

stackloss<- mutate(stackloss, relacion_Temp_Func=Water.Temp/Air.Flow)

summarise(stackloss, promedio=mean(relacion_Temp_Func))

c<- filter(stackloss, Water.Temp>18 & Water.Temp<24)
c %>% summarise(desviacion=sd(Water.Temp))

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
